---
title: "Slides Chapter6"
format: pptx
editor: visual
---

## Contents

• K-means clustering

• LDA topicmodel

• Unsupervised Scaling: Wordfish

Notes:

EUSpeech dataset

From Words to Vectors: word embeddings

kmeans and lda models

saving datasets in R (different formats)

## Machine learning in R

-   preprocessing eg. lda

-   model choice

-   model parameters: finding k (lda and kmeans),...(rest in ch7)

-   model evaluation (ch7

-   model visualization (ch4

-   

## What is k-means?

## k-means in R

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
set.seed(234)
kmeans_clusters <- kmeans(stand_embeddings, centers = 4, iter,
max = 40, nstart = 1, algorithm = "Hartigan-Wong", trace=F)
```

From Words to Vectors

-   k-means requires a matrix instead of text

k-menas: elbow plot

## LDA

what it is/ package options

code for model, use dtm!

```{r}
library(topicmodels)
```

## Homework Questions

Read the case study Scaling member of parliament positions based on Twitter data by Marius Sältzer

### Homework Exercises
