---
title: "QTA Using R"
subtitle: "Chapter 1: Calculating with Letters"
author: "Julian Bernauer and Anna Wohlmann"
date: "Spring 2025"
output: 
  ioslides_presentation:
    incremental: false
    widescreen: false 
    smaller: false 
---

```{r "knitr config", cache = FALSE, include=TRUE, echo = FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(quanteda)
library(readtext)
library(quanteda.textplots)
#opts_knit$set(root.dir = "C:/DRJB/QTA Kurs CDSS/")
```


## Agenda 

- Jumpstart QTA with the help of an example using political text
- A brief tour of the book
- Introduction to the accompanying web resources and learning features
- The building blocks of QTA and the brilliant quanteda R package
- The tidyverse R package
- A Git/GitHub primer


# Jumpstart QTA with the help of an example using political text

Word Cloud Manifesto *Bündnis Sahra Wagenknecht (BSW)*

```{r, include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# R libraries
library(quanteda)
library(readtext)
library(quanteda.textplots)
# Reading text into a data frame object named 'sahra'
# sahra <- readtext(paste0(getwd(), "/Data/chapter1/bsw_website_231027.txt"), encoding="UTF-8")
sahra <- readtext("C:/Users/homeoffice/OneDrive - uni-mannheim.de/SAGE-QTAUR/SAGE-QTAUR/Data/chapter1/bsw_website_231027.txt", encoding="UTF-8")
# sahra <- readtext("https://raw.github.com/julianbernauer/SAGE-QTAUR/tree/master/Data/chapter1/bsw_website_231027.txt", encoding="UTF-8")
# Preparing the text
sahra_dfm_trim <- dfm_remove(dfm(tokens(corpus(sahra),
                                      remove_punct = TRUE)),
                             stopwords(language = "de"))
# A word cloud
textplot_wordcloud(sahra_dfm_trim,
                   max_words = 100,
                   color = "black")
```



#  A brief tour of the book

- Chapter 1: Calculating with Letters
- Chapter 2: Using R for Text Analysis
- Chapter 3: Text as Data
- Chapter 4: Extracting and Visualising Information from Text
- Chapter 5: Supervised Machine Learning for Text Data
- Chapter 6: Unsupervised Machine Learning for Text Data
- Chapter 7: Evaluation and Validation of Quantitative Text Analysis
- Chapter 8: Using Python within R for Quantitative Text Analysis
- Chapter 9: Communicating Text Analysis



3. Web resources and learning features


## GitHub




4. Building blocks of QTA in R 
# Building blocks of QTA in R 

triad of R, RStudio and quanteda as major tools



5. quanteda
6. Tidyverse 
7. GitHub 


## DFM 

Two things to know early on are the corpus and the document-feature matrix (dfm).
A corpus is an ‘object containing the original texts, document-level variables,
document-level metadata, corpus-level metadata, and default settings for subsequent
processing of the corpus’ (see https://quanteda.io/reference/corpus.html). A dfm can
be created after taking the tokens (often, words) from a text. The matrix contains the
word count per text and is a typical starting point for a bag-of-words (BOW) analysis.



## quanteda

- Ken Benoit








## Boxes 

- Alert Box: Warns of potential pitfalls in R or QTA
- Definition Box: Introduces, defines or clarifies terms
- Knowledge Box: Basic knowledge in R that can help you move on in any
direction
- Advanced Knowledge Box: Going into more detail; not necessarily required for
following the story of the book (can be skipped)

## Tidyverse





## That's All! 

THANK YOU!

*Contact [TEACHER]*

- [Position]
- [Email]
- [FON]
- [GitHub]
- [Bluesky]
