---
title: "Chapter 4 Exercises"
author: "Anna Wohlmann and Julian Bernauer"
date: "2024-03-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1) Plot the count of animals in each order occurring in the dataset, and make sure the axis labels are readable.
```{r}
library(ggplot2)
ggplot(msleep, aes(order)) + 
  geom_bar() +
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```

2) Show the relationship between being awake and brain weight.
Include the variable "vore" in your plot using colours.
Choose four types of green based on their hex code for colours;
you can find them through this tool: https://htmlcolorcodes.com/

Hint: "colour" and "fill" have similar functions, so their adjustment works similarly.

```{r}
noNA_data <- na.omit(msleep)
ggplot(noNA_data, aes(x = awake, y = brainwt, colour = vore))+
  scale_colour_manual(values = c("#65AB67", "#10C715", "#0C750F", "#365637")) + #you can choose different tones here
  geom_point() +  xlab("Time Awake") +
  ylab("Brain Weight") +
  ggtitle("Brain Weight and time awake")
```

3) Choose another dataset from the *ggplot2* datasets and check out the variables. What would be interesting to see graphically?
Play with different graphs and design choices to make the information as clear as possible.
If necessary, use *dplyr* to bring the data into the right format.

No solution, because you choose your own data.
Obtain data through:
```{r}
data()
```

