---
title: "Chapter2_exercises"
author: "Julian Bernauer"
date: "Last edited: 2025-06-23"
output:
  pdf_document: default
  word_document: default
---


1. Install and load the quanteda package into R. Call the help function for the package
and have a look.

```{r}
install.packages("quanteda")   
library(quanteda)
help(package = "quanteda")  
```

Note:
- Before you can install the package, you need to have R and for convenience some editor on your computer.
- Be aware that quanteda is split into several sub-packages, where quanteda.textmodels, quanteda.textstats, and quanteda.textplots provide additional functionality. Check out https://quanteda.io/ for more information such as the development of quanteda.sentiment and quanteda.tidy. 
- Select a CRAN mirror that is close to your location when installing packages. In RStudio, you can also click on the Packages tab in the bottom right corner and search for quanteda.


2. Create a few text files of your choosing and read them into R with the readtext()
command. Convert the data frame object into a corpus and summarise what you have.

- Example text files could be journal abstracts, poems, or any other text you find interesting. You can create these files in a text editor and save them with a .txt extension.

The readtext command: 

```{r}
library(readtext)
practice_texts <- readtext("C:/Users/homeoffice/OneDrive - uni-mannheim.de/SAGE-QTAUR/SAGE-QTAUR/Data/chapter1/exercise1_2/", encoding = "UTF8")
practice_texts
```

Create a corpus from the data frame:
```{r}
practice_corpus <- corpus(practice_texts)
summary(practice_corpus)
```

- Alternatively, use R to create a character vector with multiple texts: 

```{r}
texts <- c("This is the first text. It is quite short.",
            "Here is another text. It is a bit longer than the first one.",
            "Finally, this is the third text. It contains more information and is the longest of all three.")
doc_id <- c("text1", "text2", "text3")
df_texts <- data.frame(doc_id = doc_id, text = texts, stringsAsFactors = FALSE)
df_texts
```

3. Convert the corpus into a dfm, remove stopwords and display a word cloud. Does it tell
you something meaningful about the texts?

