---
title: "exercises_ch4"
author: "Anna Wohlmann"
date: "2024-03-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1) Plot the count of animals in each order occurring in the dataset, and make sure the axis labels are readable.
```{r}
ggplot(msleep, aes(order)) + 
  geom_bar() +
   theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```

2) Show the relationship between being awake and brain weight.
Include the variable "vore" in your plot using colours.
Choose four types of green based on their hex code for colours;
you can find them through this tool: https://htmlcolorcodes.com/

Hint: "colour" and "fill" have similar functions, so their adjustment works similarly.

```{r}
noNA_data <- na.omit(msleep)
ggplot(noNA_data, aes(x = awake, y = brainwt, colour = vore))+
  scale_colour_manual(values = c("#65AB67", "#10C715", "#0C750F", "#365637")) + #you can choose different tones here
  geom_point() +  xlab("Time Awake") +
  ylab("Brain Weight") +
  ggtitle("Brain Weight and time awake")
```

3) No solution, because you choose your own data.
Obtain data through:
```{r}
data()
```

